A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-18 sections/conclusion/main.tex
Add changes to conclusion
- Rewrite the major contributions of the paper
- Add closed-form of steady state as area for further work

The motivation behind this study has been that emergency departments are 
under a lot of pressure to satisfy some regulations. 
This paper shows how this can negatively impact the pathway of both the 
ambulance patients and the ambulance service itself.
Due to some managerial decision making that takes place at the ED, ambulances 
stay blocked outside of the ED at the hospital's parking zone in an attempt
to satisfy these regulations.

@@

The model presented here assumes the presence of two players that can receive 
individuals. 
However, in a realistic healthcare scenario an ambulance may have to decide 
among multiple EDs.
An immediate extension of this work would be to consider a multiplayer system
that could represent a group of hospitals in a concentrated area.
Additionally, the game theoretic model that was created uses a discrete 
strategy space for the EDs (something that is also present in various related 
literature~\cite{deo2011centralized, knight2017measuring}).
The single threshold parameter that is used for the ED's decision may not be 
the best way to describe the model.
In reality ED managers could have far more complex parameters for their 
decision making process.
Finally this work assumes that the EMS and EDs act in a selfish and rational
way by only aiming to satisfy their own objectives.
In fact, modelling behaviour in a healthcare setting is a much more complex 
task where some cooperation may often be observed.
Another extension would be to explore the behaviour of the ED staff via an 
agent-based model. 
This in turn can be used to model ED staff as agents each with their own 
behavioural traits.

>>>>

The motivation behind this study has been that emergency departments are
under a lot of pressure to satisfy some regulations.
This paper shows how this can negatively impact the pathway of both the
ambulance patients and the ambulance service itself.
Due to some managerial decision making that takes place at the ED, ambulances
stay blocked outside of the ED at the hospital's parking zone in an attempt
to satisfy these regulations.
The main contributions of this paper are:
\begin{itemize}
    \item A queueing model with 2 consecutive waiting spaces where one would
    serve as a parking space for the ambulances
    \item Analytic performance measure formulas for the queueing model
    \item A 3-player game theoretic model between the EMS and two EDs
    \item Numerical experiments showing emergent behaviour of gaming between
    EDs and the EMS.
\end{itemize}

@@

The model presented here assumes the presence of two players that can receive
individuals.
However, in a realistic healthcare scenario an ambulance may have to decide
among multiple EDs.
An immediate extension of this work would be to consider a multiplayer system
that could represent a group of hospitals in a concentrated area.
Additionally, the game theoretic model that was created uses a discrete
strategy space for the EDs (something that is also present in various related
literature~\cite{deo2011centralized, knight2017measuring}).
The single threshold parameter that is used for the ED's decision may not be
the best way to describe the model.
In reality ED managers could have far more complex parameters for their
decision making process.
Moreover this work assumes that the EMS and EDs act in a selfish and rational
way by only aiming to satisfy their own objectives.
In fact, modelling behaviour in a healthcare setting is a much more complex
task where some cooperation may often be observed.
Another extension would be to explore the behaviour of the ED staff via an
agent-based model.
This in turn can be used to model ED staff as agents each with their own
behavioural traits.
Finally, future work can touch upon the derivation of a closed form formula for
the steady state probability vector of the queueing model
(section \ref{sec:queueing_model}) to allow for faster computations of \(\pi\).
